---
title: "R Notebook"
output:
  html_notebook: default
  html_document:
    df_print: paged
  word_document: default
---

In this Project,we are going to observe the time difference between querying the database with the SQL Syntax and querying the database with the dplyr syntax.  

```{r}
#Creating con in-memory RSQLite database
library(dplyr)
library(RSQLite)
con <- dbConnect(RSQLite::SQLite(), dbname = ":memory:")

#Coping flight dataset from R library to RSQlite database
copy_to(con, nycflights13::flights, "flights",
        temporary = FALSE, 
        indexes = list(
          c("year", "month", "day"), 
          "carrier", 
          "tailnum",
          "dest"
        )
)
```

```{r}
dbListTables(con)
```
```{r}
#Column variables of the flights dataset
dbListFields(con, "flights")
```
```{r}
#Reading the dataset
dbReadTable(con,"flights")
```
```{r}
#Selecting the month where month=1 from the SQL syntax
start=proc.time()
request=dbSendQuery(con, "SELECT * FROM flights WHERE month = 1")
dbFetch(request)
sleep_for_a_minute <- function() { Sys.sleep(60) }
time=proc.time()-start
time


```
We will use elapsed time for data analysis.
time=0.60 Sec
Using Dplyr
```{r}
#Selecting the month where month=1 from the dplyr syntax
library(nycflights13)
library(tidyverse)
start_1=proc.time()
filter(flights,month==1)
dplyr_filtertime=proc.time()-start_1
dplyr_filtertime
```
Time=0.30 sec
```{r}
#Selecting month, year and day from SQL syntax
start=proc.time()
request=dbSendQuery(con, "SELECT month, year, day FROM flights ")
dbFetch(request)
sleep_for_a_minute <- function() { Sys.sleep(60) }
time=proc.time()-start
time

```
Time=0.45 Sec
```{r}
#Selecting month, year and day from dplyr syntax
library(nycflights13)
library(tidyverse)
start_1=proc.time()
select(flights,month ,year,day)
dplyr_filtertime=proc.time()-start_1
dplyr_filtertime
```
Time=0.18 Sec

                     	 
Selecting a value from column(SQL Syntax(Time in Sec))	         0.60	            

Selecting a value from column(dplyr Syntax(Time in Sec))         0.30

Selecting 3 columns ((SQL Syntax(Time in Sec))	                 0.45	            

Selecting 3 columns ((dplyr Syntax(Time in Sec))	               0.18




