---
title: "R Notebook"
output: html_notebook
---

```{r}
#Importing the documents 
library(readr)
train <- read_csv("C:/Users/chink/Google Drive/Computational Statistics/Kaggle/Jan2018/train.csv")

test <- read_csv("C:/Users/chink/Google Drive/Computational Statistics/Kaggle/Jan2018/test.csv")
```

```{r}
#Checking for header
head(train)
```


```{r}
#Structure of the data
str(train)
```
```{r}
#Structure of test dataset
str(test)
```
```{r}
#Summary of training and test data
summary(train)
```
```{r}
summary(test)
```

```{r}
#Checking for missing value
library(Amelia)
missmap(train)
```
From the plot, we can observe that no missing information in training dataset.

```{r}
#Checking for missing data in test
library(Amelia)

missmap(test)
```

No missing data.

```{r}
library(gridExtra)
library(ggplot2)
p1=ggplot(train,aes(x=percent_atom_al))+geom_histogram(col="red",aes(fill=..count..))+ scale_fill_gradient("Count", low = "green", high = "blue")+labs(title="Histogram for percent_atom_al")

p2=ggplot(train,aes(x=percent_atom_ga))+geom_histogram(col="red",aes(fill=..count..))+ scale_fill_gradient("Count", low = "green", high = "blue")+labs(title="Histogram for percent_atom_ga")

p3=ggplot(train,aes(x=percent_atom_in))+geom_histogram(col="red",aes(fill=..count..))+ scale_fill_gradient("Count", low = "green", high = "blue")+labs(title="Histogram for percent_atom_in")

p4=ggplot(train,aes(x=lattice_vector_1_ang))+geom_histogram(col="red",aes(fill=..count..))+ scale_fill_gradient("Count", low = "green", high = "blue")+labs(title="Histogram for lattice_vector_1_ang")

p5=ggplot(train,aes(x=lattice_vector_2_ang))+geom_histogram(col="red",aes(fill=..count..))+ scale_fill_gradient("Count", low = "green", high = "blue")+labs(title="Histogram for lattice_vector_2_ang")

p6=ggplot(train,aes(x=lattice_vector_3_ang))+geom_histogram(col="red",aes(fill=..count..))+ scale_fill_gradient("Count", low = "green", high = "blue")+labs(title="Histogram for lattice_vector_3_ang")

p7=ggplot(train,aes(x=lattice_angle_alpha_degree))+geom_histogram(col="red",aes(fill=..count..),breaks=seq(80,110,by=1))+ scale_fill_gradient("Count", low = "green", high = "blue")+labs(title="Histogram for lattice_angle_alpha_degree")

p8=ggplot(train,aes(x=lattice_angle_beta_degree))+geom_histogram(col="red",aes(fill=..count..),breaks=seq(80,110,by=1))+ scale_fill_gradient("Count", low = "green", high = "blue")+labs(title="Histogram for lattice_angle_beta_degree")

p9=ggplot(train,aes(x=lattice_angle_gamma_degree))+geom_histogram(col="red",aes(fill=..count..),breaks=seq(80,110,by=1))+ scale_fill_gradient("Count", low = "green", high = "blue")+labs(title="Histogram for lattice_angle_gamma_degree")

p10=ggplot(train,aes(x=formation_energy_ev_natom))+geom_histogram(col="red",aes(fill=..count..))+ scale_fill_gradient("Count", low = "green", high = "blue")+labs(title="Histogram for formation_energy_ev_natom")

grid.arrange(p1,p2,p3,p4,ncol=2,nrow=2)

```

```{r}
grid.arrange(p5,p6,ncol=2,nrow=1)
```
```{r}
grid.arrange(p7,p8,ncol=2,nrow=1)
```
```{r}
grid.arrange(p9,p10,ncol=2,nrow=1)
```
```{r}
#Converting variables as factor 
train$spacegroup=as.factor(train$spacegroup)
train$number_of_total_atoms=as.factor(train$number_of_total_atoms)
```

```{r}

#Scatterplot of varaibles
s1=ggplot(train,aes(percent_atom_al,percent_atom_ga,col=spacegroup))+geom_point()+geom_smooth()+facet_wrap(~number_of_total_atoms)

s2=ggplot(train,aes(percent_atom_al,percent_atom_in,col=spacegroup))+geom_point()+geom_smooth()+facet_wrap(~number_of_total_atoms)

s3=ggplot(train,aes(percent_atom_ga,percent_atom_in,col=spacegroup))+geom_point()+geom_smooth()+facet_wrap(~number_of_total_atoms)

s1
s2
s3
```
```{r}
#Plot
s4=ggplot(train,aes(percent_atom_ga,bandgap_energy_ev,col=spacegroup))+geom_point()+facet_wrap(~number_of_total_atoms)
s4
```

```{r}
#plots
s5=ggplot(train,aes(percent_atom_al,bandgap_energy_ev,col=spacegroup))+geom_point()+facet_wrap(~number_of_total_atoms)
s5
```

```{r}
#plots
s6=ggplot(train,aes(percent_atom_in,bandgap_energy_ev,col=spacegroup))+geom_point()+facet_wrap(~number_of_total_atoms)
s6

```
```{r}
#plots
s7=ggplot(train,aes(lattice_vector_1_ang,bandgap_energy_ev,col=spacegroup))+geom_point()+facet_wrap(~number_of_total_atoms)
s7
```
```{r}
#plots
s8=ggplot(train,aes(lattice_vector_2_ang,bandgap_energy_ev,col=spacegroup))+geom_point()+facet_wrap(~number_of_total_atoms)
s8
```
```{r}
#plots
s9=ggplot(train,aes(lattice_vector_3_ang,bandgap_energy_ev,col=spacegroup))+geom_point()+facet_wrap(~number_of_total_atoms)
s9
```
```{r}
#plots
s10=ggplot(train,aes(lattice_angle_alpha_degree,bandgap_energy_ev,col=spacegroup))+geom_point()+facet_wrap(~number_of_total_atoms)
s10
```
```{r}
#plots
s11=ggplot(train,aes(lattice_angle_beta_degree,bandgap_energy_ev,col=spacegroup))+geom_point()+facet_wrap(~number_of_total_atoms)
s11
```
```{r}
#plots
s12=ggplot(train,aes(lattice_angle_gamma_degree,bandgap_energy_ev,col=spacegroup))+geom_point()+facet_wrap(~number_of_total_atoms)
s12
```
```{r}
#plots
s13=ggplot(train,aes(formation_energy_ev_natom,bandgap_energy_ev,col=spacegroup))+geom_point()+facet_wrap(~number_of_total_atoms)
s13
```

```{r}
#Subsetting the data by spacegroup
spacegroup33= train[which(train$spacegroup == "33"),]
summary(spacegroup33)
```
```{r}
#Subsetting the data by spacegroup
spacegroup12= train[which(train$spacegroup == "12"),]
summary(spacegroup12)
```

```{r}
#Subsetting the data by spacegroup
spacegroup167= train[which(train$spacegroup == "167"),]
summary(spacegroup167)
```
```{r}
#Subsetting the data by spacegroup
spacegroup194= train[which(train$spacegroup == "194"),]
summary(spacegroup194)
```
```{r}
#Subsetting the data by spacegroup
spacegroup206= train[which(train$spacegroup == "206"),]
summary(spacegroup206)
```
```{r}
#Subsetting the data by spacegroup
spacegroup227= train[which(train$spacegroup == "227"),]
summary(spacegroup227)
```
```{r}
#Investigate the bandgap_energy_ev of diamonds using box plots
ggplot(train,aes(factor(spacegroup),bandgap_energy_ev,fill=spacegroup))+geom_boxplot()
```
```{r}
#Investigate the bandgap_energy_ev of diamonds using box plots
ggplot(train,aes(factor(number_of_total_atoms),bandgap_energy_ev,fill=number_of_total_atoms))+geom_boxplot()
```
```{r}
#Table
head(sort(table(train$spacegroup),decreasing = T))
```
```{r}
#Table
head(sort(table(train$number_of_total_atoms),decreasing = T))
```

```{r}
#mtcars is a data frame 
library(corrplot)
train$spacegroup=as.numeric(train$spacegroup)
train$number_of_total_atoms=as.numeric(train$number_of_total_atoms)
t=cor(train)
corrplot(t, order = "AOE")

```
```{r}
#Step function
full=lm(bandgap_energy_ev~.-(spacegroup+number_of_total_atoms+id+formation_energy_ev_natom)+factor(spacegroup)+factor(number_of_total_atoms),data=train)
null=lm(bandgap_energy_ev~1,data=train)
step(null, scope=list(lower=null, upper=full),
direction="forward")

```
Low AIC model is lm(formula = bandgap_energy_ev ~ percent_atom_in + factor(spacegroup) + 
    percent_atom_ga + lattice_angle_alpha_degree + factor(number_of_total_atoms) + 
    lattice_vector_1_ang + lattice_vector_3_ang + percent_atom_al + 
    lattice_angle_beta_degree, data = train)

    
```{r}
#Linear Regression model
train$spacegroup=as.factor(train$spacegroup)
train$number_of_total_atoms=as.factor(train$number_of_total_atoms)
m1=lm(formula = bandgap_energy_ev ~ percent_atom_in + factor(spacegroup) + 
    percent_atom_ga + lattice_angle_alpha_degree + factor(number_of_total_atoms) + 
    lattice_vector_1_ang + lattice_vector_3_ang + percent_atom_al + 
    lattice_angle_beta_degree, data = train)

summary(m1)
```
```{r}
#Checking model dignostics 
r=residuals(m1)
plot(r,col="green")
```
 Plot of residuals are scattered around. Errors are normaliy distributed.
 
```{r}
# Normality test
shapiro.test(r) 

```
 
As w>95%. Normality assumption is satisfied.
```{r}
#Removing id colunm
test=test[-1,]
test$spacegroup=as.factor(test$spacegroup)
test$number_of_total_atoms=as.factor(test$number_of_total_atoms)

```

